Poseidon Adventure

### 2019-06-11 TestCalcZ2.Rmd
calc Z further work

Time to step through line by line again.

@@

  # merge recruits with strucn and resn of recruits from biol.prm file
  recruits <- merge(recruits, nitro[, c(1, 4)],
    by.x = "group", by.y = "1", all.x = TRUE, all.y = FALSE)
  colnames(recruits)[which(colnames(recruits) == "recruits")] <- "recruitsbio"
  # Get recruits in numbers rather than biomass
  recruits$recruits <- recruits$recruitsbio / recruits$sum

@@

  recstart_temp <- rectiming[rectiming$Code %in% recruits$group,]

@@

  recruits$frac_recruit <- 0
  for (irow in 1:nrow(recstart_temp)) {
    group <- recstart_temp$Code[irow]
    pick <- which(recruits$group == group)

    recstart <- seq(recstart_temp$recstart[irow],by=365,length.out=nyrs)
    recstart <- recstart[recstart<max(recruits$Time[pick])]
    recend <- recstart + recstart_temp$recend[irow]
    #rec_times <- rbind(rec_times,cbind(group,recstart,recend))

    # this part still returns a constant fraction
    # and does not alter Time to change from annual to actual recruitment time
    # still not understanding what this is meant to do
    for (i_rec in 1:length(recstart)) {
      i_tstart <- which(pick==min(pick[recruits$Time[pick]>=recstart[i_rec]]))
      i_tstop <- which(pick==min(pick[recruits$Time[pick]>=recend[i_rec]]))
      if (i_rec == length(recstart)) i_tstop <- length(pick)
      n_t <- 1+i_tstop-i_tstart
      for (i_t in 1:n_t) {
        t_temp <- recruits$Time[pick[i_tstart+i_t-1]]
        num_temp <- t_temp - recstart[i_rec]
        if (i_t>1) {
          if ((recend[i_rec]-t_temp)>toutinc) {
            num_temp <- toutinc
          }
          else {
            num_temp <- recend[i_rec]-(recruits$Time[pick[i_tstart+i_t-2]])
          }
        }
        frac_temp <- max(c(0,num_temp /(recend[i_rec]-recstart[i_rec])))
        recruits$frac_recruit[pick[i_tstart+i_t-1]] <- frac_temp
      }
    }
  }

# Time in YOY does not match recstart-recend period still after this loop

  # match "Time" of the young of the year with the time-step periodicity
  # listed in the run.prm or run.xml file
  recruits$Time <- recruits$Time / toutinc

# SKG did this above already in the following line?
  # Get recruits in numbers rather than biomass
  #recruits$recruits <- recruits$recruitsbio / recruits$sum
  #G.Fay 1/6/16, expand to num of recruits
  # Recruit / mg C converted to wet weight in tonnes / redfield ratio of C:N
  #recruits$recruits <- recruits$recruits/k_wetdry/biolprm$redfieldcn

  # Sum over all boxes/depth/cohorts
  totnums <- aggregate(atoutput ~ species + time, data = nums, sum)

  # Combine recruits and numbers
  # Only pull recruits from the yearly time step, where the
  # yearly time step matches the time step
  totnums <- merge(totnums, recruits,
    by.x = c("time", "species"), by.y = c("Time", "Name"),
    all.x = TRUE, all.y = FALSE)
  totnums$group <- recruits$group[match(totnums$species, recruits$Name)]
  # For all time increments where there
  totnums$recruits[is.na(totnums$recruits)] <- 0

  # Calculate survivors for each species group
  totnums$survivors <- totnums$recruits
  # Make sure time is in order
  totnums <- totnums[order(totnums$species, totnums$time), ]

  totnums$recruits <- totnums$recruits*totnums$frac_recruit

>>>>

Time to step through line by line again. Revised as below. Better (apportions annual recruitment to timesteps), but not sure this is fully correct?

@@

  # merge recruits with strucn and resn of recruits from biol.prm file
  recruits <- merge(recruits, nitro[, c(1, 4)],
    by.x = "group", by.y = "1", all.x = TRUE, all.y = FALSE)
  colnames(recruits)[which(colnames(recruits) == "recruits")] <- "recruitsbio"
  # Get recruits in numbers rather than biomass
  # these match rows 2:end of the legacy file, so good
  # but is this 1000s or numbers? not real numbers, Gavin corrects below
  recruits$recruits <- recruits$recruitsbio / recruits$sum
  recruits$yr <- as.integer(round(recruits$Time)/365)

@@

  #subsets to groups of interest
  recstart_temp <- rectiming[rectiming$Code %in% recruits$group,]

@@

  # align model output timesteps (days) with recruitment periods (days)
  numstime.days <- unique(nums$time)*toutinc
  # Sum numbers output over all boxes/depth/cohorts
  totnums <- aggregate(atoutput ~ species + time, data = nums, sum) %>%
    mutate(time.days = time*toutinc) %>%
    mutate(yr = floor(time.days/365))

  totnums <- merge(totnums, recruits,
    by.x = c("yr", "species"), by.y = c("yr", "Name"),
    all.x = TRUE) %>%
    arrange(time)

  totnums$frac_recruit <- 0

  for (irow in 1:nrow(recstart_temp)) {
    group <- recstart_temp$Code[irow]
    pick <- which(totnums$group == group)

    recstart <- seq(recstart_temp$recstart[irow],by=365,length.out=nyrs)
    recstart <- recstart[recstart<max(totnums$Time[pick])]
    recend <- recstart + recstart_temp$recend[irow]
    #rec_times <- rbind(rec_times,cbind(group,recstart,recend))

    for (i_rec in 1:length(recstart)) {
      i_tstart <- which(pick==min(pick[numstime.days[pick]>=recstart[i_rec]]))
      i_tstop <- which(pick==min(pick[numstime.days[pick]>=recend[i_rec]]))
      if (i_rec == length(recstart)) i_tstop <- length(pick)
      n_t <- 1+i_tstop-i_tstart
      for (i_t in 1:n_t) {
        t_temp <- numstime.days[pick[i_tstart+i_t-1]]
        num_temp <- t_temp - recstart[i_rec]
        if (i_t>1) {
          if ((recend[i_rec]-t_temp)>toutinc) {
            num_temp <- toutinc
          }
          else {
            num_temp <- recend[i_rec]-(numstime.days[pick[i_tstart+i_t-2]])
          }
        }
        frac_temp <- max(c(0,num_temp /(recend[i_rec]-recstart[i_rec])))
        totnums$frac_recruit[pick[i_tstart+i_t-1]] <- frac_temp
      }
    }
  }

# Time in YOY does not match recstart-recend period still after this loop--fixed

  # match "Time" of the young of the year with the time-step periodicity
  # listed in the run.prm or run.xml file
  #recruits$Time <- recruits$Time / toutinc

# SKG did this above already in the following line?
  # Get recruits in numbers rather than biomass
  #recruits$recruits <- recruits$recruitsbio / recruits$sum

  #G.Fay 1/6/16, expand to num of recruits
  # Recruit / mg C converted to wet weight in tonnes / redfield ratio of C:N
  totnums$recruits <- totnums$recruits/k_wetdry/biolprm$redfieldcn

  # Combine recruits and numbers
  # Only pull recruits from the yearly time step, where the
  # yearly time step matches the time step
  # totnums <- merge(totnums, recruits,
  #   by.x = c("time", "species"), by.y = c("Time", "Name"),
  #   all.x = TRUE, all.y = FALSE)
  totnums$group <- recruits$group[match(totnums$species, recruits$Name)]
  # For all time increments where there
  totnums$recruits[is.na(totnums$recruits)] <- 0

   # Make sure time is in order, did above
  #totnums <- totnums[order(totnums$species, totnums$time), ]
  totnums$annrecruits <- totnums$recruits

  totnums$recruits <- totnums$annrecruits*totnums$frac_recruit

  # Calculate survivors for each species group
  totnums$survivors <- totnums$recruits

### 2019-06-11 docs/index.Rmd
initial comparisons calc Z with mort.txt
calc Z further work

>>>>

June 7: `calc_Z` seems incorrect when compared to outputMort.txt; stepping through code needed

June 11: fixed matching of recruitment to timestep, still seems off

<a href="https://sgaichas.github.io/poseidon-dev/TestCalcZ2.html" target="_blank">Test Z calc and compare with output mort CCA - June 7, 2019, updated June 11</a>
